Interactively Visualizing Multivariate Market Segmentation Using the R Package Lionfish

### 2024-10-03 manuscript.tex
shifted reference to website into own section

More information on all the features of the GUI can be found on \href{https://github.com/mmedl94/lionfish}{https://github.com/mmedl94/lionfish} and on \href{https://mmedl94.github.io/lionfish/}{https://mmedl94.github.io/lionfish/}.

@@

>>>>

@@

\section{Resources and supplementary materials}~\label{resources}

The software can be found at  \href{https://mmedl94.github.io/lionfish/}{https://mmedl94.github.io/lionfish/} which contains more documentation on:

\begin{itemize} \itemsep 0in
\item installation
\item currently supported interactivity
\item the variety of plots available
\end{itemize}

The supplementary materials for this paper include:

\begin{itemize} \itemsep 0in
\item scripts to start the GUI and reproduce the graphics in the paper
\item saved state for different parts of the applications, so that the results can be reproduced
\end{itemize}
